Probing the internal structures of quasars using microlensing events

### 2016-03-14 paper1/discussion.tex
Discussion paragraph switching

With the different source profiles and their corresponding lightcurves studied we can change our point of view of the system to that of an observer. The observer would basically detect only the lightcurve of such as source. As described in section 4.3 (Lightcurve of a crescent shaped source) the timing of the onset and offset of the previously described periods can be used to estimate the values of the radii and one of the displacement parameters when assuming a geometric crescent. All quantities can be estimated in terms of the relative velocity of the source in a direction perpendicular to the caustic.\\

The previously mentioned abstract parameters can be related to physical quantities specific to the central region of a quasar. Thus the luminous region would correspond to the bright accretion disc that surrounds the black hole. The later's gravity would cause a shadow in the bright region limited by the extent of the event horizon of the black hole. \textbf{Therefore the radius of the bright disk would provide an estimate of the size of the accretion disk and the radius of the dark disc would provide and estimate of the gravitationally magnified Schwarzschild radius of the black hole $R_{S}^{magnified} = \Delta t_{dark}*v_p$. By $R_{S}^{magnified}$ we refer to the apparent Schwarzschild radius which is larger than the real value at large distances due to the black hole's own gravity.  Moreover the gravitationally magnified value of the Schwarzschild radius is a monotonic function of the black hole's mass. Therefore it 
can be used to estimate the mass of the black hole if it was not rotating.} In the previous 
expression the $\Delta t_{dark}$ denotes the period of overlap between the black hole shadow and fold caustic. 
$v_p$ denotes the component of the relative velocity of the source and fold which is perpendicular to the caustic.  
The respective velocity is an unknown, though it can be constrained on a case by case basis to an order of magnitude or even better. This would require the 
study of the dynamics of the stellar structure which contains the gravitational lens. A better estimate of the relative velocity would facilitate a better estimate of the effective non-rotating black hole mass associated to the black hole shadow.

\textbf{In case of a high quality lightcurve with insignificant noise and measurement errors, the parameters can be obtained 
by simply identifying the characteristic instances of time without making use of the actual values of the magnification
 map. If the effect of the errors and the noise distorts the magnification time function enough so that the 
characteristic epochs are not identifiable with the characteristic periods still visible, the boundaries of the periods 
can be roughly estimated. Furthermore, if direct estimates of the parameters cannot be obtained we propose the use of a strong
statistical tool such as Markov-Chain Monte Carlo. In Section 6  we have studied the possibility of identifying a crescent 
source and  the possibility of recovering the respective parameters. As magnification map we have used a complex numerical 
one generated with the microlensing code by \cite{1999A&A...346L...5W}. In addition we have added to the signal a Gaussian 
noise with a SNR of 1.6.  In the experiment we have considered all nine combinations of original source profiles and assumed fitting source models.
Effectively we have fitted using MCMC all three sources with all three assumed fitting models. The results of the experiment allowed us build a 
procedure for distinguishing the shape of the source assuming that one of the three models we have considered is a good approximation.  
The procedure would be useful for observers that endeavour to gain more information about an unresolved source for which they can study 
the microlensing lightcurve.  As a first step in the procedure, one should first attempt to use MCMC with a Gaussian model assumption. 
If either the value of the $\chi^2$ or the number of rejected datapoints is large then the next step is to change the assumed source model to 
an uniform disc and redo the fitting. Finally if the uniform disc assumption is rejected as well then the fitting should be done with a 
crescent source model assumption. If at each of the three steps the data rejects the model then the source cannot be approximated by any of the three models. 
Otherwise if at one of the steps the data does not reject the model then the respective model is a good approximation.   }

\textbf{Furthermore, a simulated image of M87 presented in \citep{2012MNRAS.421.1517D} (figure 9) has been microlensed. On the resulting lightcurve the instances corresponding to the start and end of the black hole shadow and caustic overlap were distinguishable as can be seen in figure 10.}

>>>>

With the different source profiles and their corresponding lightcurves studied we can change our point of view of the system to that of an observer. 
The observer would basically detect only the lightcurve of such a source. As described in section 4.3 the timing of the onset and offset of the previously 
described periods can be used to estimate the values of the radii and one of the displacement parameters when assuming a geometric crescent. 
All quantities can be estimated in terms of the relative velocity of the source in a direction perpendicular to the caustic.

Furthermore, a simulated image of M87 presented in \citep{2012MNRAS.421.1517D} (figure 9) has been microlensed. On the resulting lightcurve the instances 
corresponding to the start and end of the black hole shadow and caustic overlap were distinguishable as can be seen in figure 10.

In case of a high quality lightcurve with insignificant noise and measurement errors, the parameters can be obtained 
by simply identifying the characteristic instances of time without making use of the actual values of the magnification
 map. If the effect of the errors and the noise distorts the magnification time function enough so that the 
characteristic epochs are not identifiable with the characteristic periods still visible, the boundaries of the periods 
can be roughly estimated. Furthermore, if direct estimates of the parameters cannot be obtained we propose the use of a strong
statistical tool such as Markov-Chain Monte Carlo. In Section 6  we have studied the possibility of identifying a crescent 
source and  the possibility of recovering the respective parameters. As magnification map we have used a complex numerical 
one generated with the microlensing code by \cite{1999A&A...346L...5W}. In addition we have added to the signal a Gaussian 
noise with a SNR of 1.6.  In the experiment we have considered all nine combinations of original source profiles and assumed fitting source models.
Effectively we have fitted using MCMC all three sources with all three assumed fitting models. The results of the experiment allowed us build a 
procedure for distinguishing the shape of the source assuming that one of the three models we have considered is a good approximation.  
The procedure would be useful for observers that endeavour to gain more information about an unresolved source for which they can study 
the microlensing lightcurve.  As a first step in the procedure, one should first attempt to use MCMC with a Gaussian model assumption. 
If either the value of the $\chi^2$ or the number of rejected datapoints is large then the next step is to change the assumed source model to 
an uniform disc and redo the fitting. Finally if the uniform disc assumption is rejected as well then the fitting should be done with a 
crescent source model assumption. If at each of the three steps the data rejects the model then the source cannot be approximated by any of the three models. 
Otherwise if at one of the steps the data does not reject the model then the respective model is a good approximation.

The previously mentioned abstract parameters can be related to physical quantities specific to the central region of a quasar. 
As such the luminous region would correspond to the bright accretion disc that surrounds the black hole. The later's gravity would 
cause a shadow in the bright region limited by the extent of the event horizon of the black hole. \textbf{Therefore the radius 
of the bright disk would provide an estimate of the size of the accretion disk and the radius of the dark disc would provide
 and estimate of the gravitationally magnified Schwarzschild radius of the black hole $R_{S}^{magnified} = \Delta t_{dark} \cdot v_p$.
By $R_{S}^{magnified}$ we refer to the apparent Schwarzschild radius which is larger than the real value at large distances due to the
black hole's own gravity.  Moreover the gravitationally magnified value of the Schwarzschild radius is a monotonic function of the black 
hole's mass. Therefore it can be used to estimate the mass of the black hole if it was not rotating.} In the previous 
expression the $\Delta t_{dark}$ denotes the period of overlap between the black hole shadow and fold caustic. 
$v_p$ denotes the component of the relative velocity of the source and fold which is perpendicular to the caustic.  
The respective velocity is an unknown, though it can be constrained on a case by case basis to an order of magnitude 
or even better. This would require the study of the dynamics of the stellar structure which contains the gravitational lens. 
A better estimate of the relative velocity would facilitate a better estimate of the effective non-rotating black hole 
mass associated to the black hole shadow.
